---
title: "p8105_hw1_xt2288"
output: github_document
date: "2023-09-15"
---

## Problem 1

```{r}
library(moderndive)
data("early_january_weather")
```

The dataset has 15 variables, which are origin(weather station), year, month, day, hour(time of recording), temp(temperature in F), dewp(dewpoint in F), humid(relative humidity), wind_dir(wind direction in degrees), wind_speed(wind speed in mph), wind_gust(gust speed in mph), precip(precipitation in inches), pressure(sea level pressure in millibars), visib(visibility in miles), and time_hour(date and hour of the recording).
The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 
The mean temperature is `r mean(early_january_weather$temp)`F.

```{r}
library(tidyverse)
```

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("problem 1 scatterplot.png")
```
In this plot, the temperature increases as day passes. The temperature doesn't change much during high humidity days.







