---
title: "p8105_hw1_xt2288"
output: github_document
date: "2023-09-15"
---

```{r}
library(moderndive)
library(tidyverse)
```


## Problem 1

```{r}
data("early_january_weather")
```

The dataset has 15 variables, which are origin(weather station), year, month, day, hour(time of recording), temp(temperature in F), dewp(dewpoint in F), humid(relative humidity), wind_dir(wind direction in degrees), wind_speed(wind speed in mph), wind_gust(gust speed in mph), precip(precipitation in inches), pressure(sea level pressure in millibars), visib(visibility in miles), and time_hour(date and hour of the recording).
The dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 
The mean temperature is `r mean(early_january_weather$temp)`F.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("problem 1 scatterplot.png")
```
In this plot, the temperature increases as day passes. The temperature doesn't change much during high humidity days.


## Problem 2

```{r}
P2_df = 
  tibble(
    ran_sam = rnorm(10),
    log_vec = ran_sam > 0,
    cha_vec = as.character(c("a","b","c","d","e","f","g","h","i","j")),
    fac_vec = factor(c("L1","L2","L3","L1","L2","L3","L1","L2","L3","L1"),
                     levels = c("L1","L2","L3"))
    )
```

```{r}
mean(pull(P2_df,var=1))
mean(pull(P2_df,var=2))
mean(pull(P2_df,var=3))
mean(pull(P2_df,var=4))
```

The first and second column can take the mean, which are numeric and logical columns. Character and factor cannot take the mean.

```{r, eval=FALSE}
as.numeric(pull(P2_df,var=2))
as.numeric(pull(P2_df,var=3))
as.numeric(pull(P2_df,var=4))
```
Logical vector can be converted to numeric values. Ture is 1 and false is 0, so the logical vector has a mean. Character vector cannot be converted to numbers. The letters in character vector does not have a numeric meaning, so no numbers can represent the characters and no mean. The numeric value of the factor vector shows the levels from 1 to 3. There is no mean for the level values as it is meaningless.




